---
title: "File Download for past MS exams"
output: html_notebook
---

# Past Statistics and Biostatistics MS exam data files

You can run this R notebook to download all of the past Statistics and Biostatistics MS exam data files.

The data files are downloaded from the MS Exam github repository.  [msexam](https://github.com/esuess/msexam/tree/master/pastmsexam)

```{r}
files <- list(
  
    d2018 = list( 
      df = list(url = "https://github.com/esuess/msexam/blob/master/pastmsexam/2018/Spring2018/",
        fs = list("ob_prob1.xlsx","sat_data.txt","lemon.csv","prob4.dat","BigMac.csv"),
        fb = list("ob_prob1.xlsx","sat_data.txt","lemon.csv","prob4.dat","uis.txt") ),
      ds = list(url = "https://github.com/esuess/msexam/blob/master/pastmsexam/2018/Spring2018/",
        ss = list("ob_prob1.csv","sat_data.txt","lemon.csv","prob4.dat","BigMac.csv"),
        sb = list("ob_prob1.csv","sat_data.txt","lemon.csv","prob4.dat","uis.txt") ) ),
  
    d2017 = list( 
      df = list(url = "https://github.com/esuess/msexam/blob/master/pastmsexam/2017/Fall2017/",
        fs = list("INJURY9.csv","river.csv","prostate.csv","prob4.txt","Jets.csv"),
        fb = list("INJURY9.csv","river.csv","prostate.csv","prob4.txt","valung.csv") ),
      ds = list(url = "https://github.com/esuess/msexam/blob/master/pastmsexam/2017/Spring2017/",
        ss = list("ob_prob1.xlsx","problem2.sas","heart.csv","sales.txt","Barley.csv"),
        sb = list("ob_prob1.xlsx","problem2.sas","heart.csv","sales.txt","breast.csv") ) ),
    
    d2016 = list(
      df = list(url = "https://github.com/esuess/msexam/blob/master/pastmsexam/2016/Fall2016/",
        fs = list("hypnotic_induction.csv","problem2.sas","mammography.csv","cars.txt","forest.csv"),
        fb = list("hypnotic_induction.csv","problem2.sas","mammography.csv","cars.txt","kidrecurr.txt") ),
      ds = list(url = "https://github.com/esuess/msexam/blob/master/pastmsexam/2016/Spring2016/",
      ss = list("cakemix.txt","problem2.csv","health.txt","DES_all.txt"),
      sb = list("cakemix.txt","problem2.csv","health.txt","selenium.csv") ) )
)



```





Specify the years of exams data file you wish to download.




First set the directory where you would like to download all of the files.

```{r}
download_dir <- "C:/Past_MS_Exams-CSUEB_Statistics_and_Biostatistics"

print(download_dir)
ifelse(!dir.exists(file.path(download_dir)), dir.create(file.path(download_dir)), 
       paste0("Directory already exists"))

#setwd(file.path(download_dir))

stat_dir <- file.path(download_dir, "Past_MS_Exams-Statistics")
stat_dir
biostat_dir <- file.path(download_dir, "Past_MS_Exams-Biostatistics")
biostat_dir

print(stat_dir)
ifelse(!dir.exists(file.path(stat_dir)), dir.create(file.path(stat_dir)), 
       paste0("Directory already exists"))

print(biostat_dir)
ifelse(!dir.exists(file.path(biostat_dir)), dir.create(file.path(biostat_dir)), 
       paste0("Directory already exists"))
```

Second create the subdirectories to download the files to.

```{r}
#stat_dir
#biostat_dir

start_year <- 2016  #1998

end_year <- 2018


years <- (end_year-start_year+1)

test <- list("Fall", "Spring")

for (i in 1: length(test)){        # spring or fall
  for (j in end_year: start_year){ # year
    DIR <- paste0(j,"_",test[[i]])
    print(DIR)
    
    # Make Statistics subdirectories
    stat_dir_new <- file.path(stat_dir, DIR)
    print(stat_dir_new)
    ifelse(!dir.exists(file.path(stat_dir, DIR)), dir.create(file.path(stat_dir, DIR)), 
           print(paste0("Directory already exists")))
    
    for (k in 1: length(files[[(end_year-j+1)]][[i]][[(2)]])) {
        download.file( paste0(   files[[(end_year-j+1)]][[i]][[1]], paste0( files[[(end_year-j+1)]][[i]][[2]][[k]] )  ),
                          paste0(file.path(stat_dir, DIR ),"/",paste0(files[[(end_year-j+1)]][[1]][[2]][[k]]))   )
    }
  
    # Make Biostat subdirectories
    biostat_dir_new <- file.path(biostat_dir, DIR)
    print(biostat_dir_new)
    ifelse(!dir.exists(file.path(biostat_dir, DIR)), dir.create(file.path(biostat_dir, DIR)), 
           print(paste0("Directory already exists")))
    
    for (k in 1: length(files[[(end_year-j+1)]][[i]][[3]])) {
        download.file( paste0(   files[[(end_year-j+1)]][[i]][[1]], paste0( files[[(end_year-j+1)]][[i]][[3]][[k]] )  ),
                          paste0(file.path(biostat_dir, DIR ),"/",paste0(files[[(end_year-j+1)]][[i]][[3]][[k]]))   )
    }
}
}

```



### MS Exam, Biostatistics, Spring 2018

```{r}

files <- list(
    d2018 = list( 
      ss = list("ob_prob1.csv", "sat_data.txt", "lemon.csv", "prob4.dat", "BigMac.csv"),
      sb = list("ob_prob1.csv", "sat_data.txt", "lemon.csv", "prob4.dat", "uis.txt") ),
  
    d2017 = list( 
      fs = list("INJURY9.csv", "river.csv", "prostate.csv", "prob4.txt", "Jets.csv"),
      fb = list("INJURY9.csv", "river.csv", "prostate.csv", "prob4.txt", "valung.csv"),
      ss = list("ob_prob1.xlsx", "problem2.sas", "heart.csv", "sales.txt", "Barley.csv"),
      sb = list("ob_prob1.xlsx", "problem2.sas", "heart.csv", "sales.txt", "breast.csv") )
)
  
files
files$d2018$ss[[1]]


"C:/Past_MS_Exams-CSUEB_Statistics_and_Biostatistics/Past_MS_Exams-Statistics/2018_Spring"

"C:/Past_MS_Exams-CSUEB_Statistics_and_Biostatistics/Past_MS_Exams-Biostatistics/2018_Spring"

stat_Spring_2018_dir <-"C:/Past_MS_Exams-CSUEB_Statistics_and_Biostatistics/Past_MS_Exams-Statistics/2018_Spring"

biostat_Spring_2018_dir <- "C:/Past_MS_Exams-CSUEB_Statistics_and_Biostatistics/Past_MS_Exams-Biostatistics/2018_Spring"


for ( i in 1: length(files$d2018$ss)){ 
  download.file(paste0("https://raw.githubusercontent.com/esuess/msexam/master/pastmsexam/2018/Spring2018/", paste0(files$d2018$ss[[i]]) ),
                file.path(stat_Spring_2018_dir, paste0(files$d2018$ss[[i]]) ) )
}

for ( i in 1: length(files$d2018$sb)){ 
  download.file(paste0("https://raw.githubusercontent.com/esuess/msexam/master/pastmsexam/2018/Spring2018/", paste0(files$d2018$sb[[i]]) ),
                file.path(biostat_Spring_2018_dir, paste0(files$d2018$sb[[i]]) ) )
}


Spring_2018_dir <- list(stat_Spring_2018_dir, biostat_Spring_2018_dir)

for (year in 2017:2018) {
for (i in 1:length(files[[1]]) ) {            # stat or biostat
  length(files[[1]])
  for (j in 1:length(files[[1]][[i]]) ) {     # spring or fall
  download.file(paste0("https://raw.githubusercontent.com/esuess/msexam/master/pastmsexam/",year,"/Spring",year,"/", paste0(files[[1]][[i]][j]) ),
                file.path(Spring_2018_dir[i], paste0(files[[1]][[i]][j])) ) 
  }
}
}


for (i in 1: length(test)){        # spring or fall
  for (j in end_year: start_year){ # year
    DIR <- paste0(j,test[[i]])
    print(DIR)
    
    # Make Statistics subdirectories
    stat_dir_new <- file.path(stat_dir, DIR)
    print(stat_dir_new)
    ifelse(!dir.exists(file.path(stat_dir, DIR)), dir.create(file.path(stat_dir, DIR)), 
           print(paste0("Directory already exists")))
    
    stat_dir_new_list[[(end_year-j)+1]][i] <- file.path(stat_dir, DIR)
    
    
    
    
    

for (year in start_year: end_year) {

for (i in 1:length(files[[1]]) ) {            # stat or biostat
  length(files[[1]])
  for (j in 1:length(files[[1]][[i]]) ) {     
  download.file(paste0("https://raw.githubusercontent.com/esuess/msexam/master/pastmsexam/",year,"/",test[i],year,"/", paste0(files[[(year-start_year+1)]][[i]][j]) ),
                file.path(dir_new_list[[(year-start_year+1)]][[i]][[(end_year-year+1)]], paste0(files[[(year-start_year+1)]][[i]][j])) ) 
  }
}

}
  

for ( i in 1: length(files$d2018$ss)){ 
  download.file(paste0("https://raw.githubusercontent.com/esuess/msexam/master/pastmsexam/2018/Spring2018/", paste0(files$d2018$ss[[i]]) ),
                file.path(stat_Spring_2018_dir, paste0(files$d2018$ss[[i]]) ) )
}

for ( i in 1: length(files$d2018$sb)){ 
  download.file(paste0("https://raw.githubusercontent.com/esuess/msexam/master/pastmsexam/2018/Spring2018/", paste0(files$d2018$sb[[i]]) ),
                file.path(biostat_Spring_2018_dir, paste0(files$d2018$sb[[i]]) ) )
 }




download.file("https://raw.githubusercontent.com/esuess/msexam/master/pastmsexam/2018/Spring2018/ob_prob1.csv", file.path(biostat_Spring_2018_dir, "ob_prob1.csv"))

download.file("https://raw.githubusercontent.com/esuess/msexam/master/pastmsexam/2018/Spring2018/sat_data.txt", file.path(biostat_Spring_2018_dir, "sat_data.txt"))

download.file("https://raw.githubusercontent.com/esuess/msexam/master/pastmsexam/2018/Spring2018/lemon.csv", file.path(biostat_Spring_2018_dir, "lemon.csv"))

download.file("https://raw.githubusercontent.com/esuess/msexam/master/pastmsexam/2018/Spring2018/prob4.dat", file.path(biostat_Spring_2018_dir, "prob4.dat"))

download.file("https://raw.githubusercontent.com/esuess/msexam/master/pastmsexam/2018/Spring2018/uis.txt", file.path(biostat_Spring_2018_dir, "uis.txt"))
```



### MS Exam, Statistics, Fall 2017

```{r}
download.file("https://raw.githubusercontent.com/esuess/msexam/master/pastmsexam/2017/Fall2017/INJURY9.csv", file.path(stat_Fall_2017_dir, "INJURY9.csv"))

download.file("https://raw.githubusercontent.com/esuess/msexam/master/pastmsexam/2017/Fall2017/river.csv", file.path(stat_Fall_2017_dir, "river.csv"))

download.file("https://raw.githubusercontent.com/esuess/msexam/master/pastmsexam/2017/Fall2017/prostate.csv", file.path(stat_Fall_2017_dir, "prostate.csv"))

download.file("https://raw.githubusercontent.com/esuess/msexam/master/pastmsexam/2017/Fall2017/prob4.txt", file.path(stat_Fall_2017_dir, "prob4.txt"))

download.file("https://raw.githubusercontent.com/esuess/msexam/master/pastmsexam/2017/Fall2017/Jets.csv", file.path(stat_Fall_2017_dir, "Jets.csv"))


download.file("https://raw.githubusercontent.com/esuess/msexam/master/pastmsexam/2017/Fall2017/INJURY9.csv", file.path(biostat_Fall_2017_dir, "INJURY9.csv"))

download.file("https://raw.githubusercontent.com/esuess/msexam/master/pastmsexam/2017/Fall2017/river.csv", file.path(biostat_Fall_2017_dir, "river.csv"))

download.file("https://raw.githubusercontent.com/esuess/msexam/master/pastmsexam/2017/Fall2017/prostate.csv", file.path(biostat_Fall_2017_dir, "prostate.csv"))

download.file("https://raw.githubusercontent.com/esuess/msexam/master/pastmsexam/2017/Fall2017/prob4.txt", file.path(biostat_Fall_2017_dir, "prob4.txt"))

download.file("https://raw.githubusercontent.com/esuess/msexam/master/pastmsexam/2017/Fall2017/valung.csv", file.path(biostat_Fall_2017_dir, "valung.csv"))

```

### MS Exam, Biostatistics, Spring 2017

```{r}
download.file("https://raw.githubusercontent.com/esuess/msexam/master/pastmsexam/2017/Spring2017/ob_prob1.csv", file.path(stat_Spring_2017_dir, "ob_prob1.csv"))

download.file("https://raw.githubusercontent.com/esuess/msexam/master/pastmsexam/2017/Spring2017/problem2.sas", file.path(stat_Spring_2017_dir, "problem2.sas"))

download.file("https://raw.githubusercontent.com/esuess/msexam/master/pastmsexam/2017/Spring2017/heart.csv", file.path(stat_Spring_2017_dir, "heart.csv"))

download.file("https://raw.githubusercontent.com/esuess/msexam/master/pastmsexam/2017/Spring2017/sales.txt", file.path(stat_Spring_2017_dir, "sales.txt"))

download.file("https://raw.githubusercontent.com/esuess/msexam/master/pastmsexam/2017/Spring2017/Barley.csv", file.path(stat_Spring_2017_dir, "Barley.csv"))


download.file("https://raw.githubusercontent.com/esuess/msexam/master/pastmsexam/2017/Spring2017/ob_prob1.csv", file.path(biostat_Spring_2017_dir, "ob_prob1.csv"))

download.file("https://raw.githubusercontent.com/esuess/msexam/master/pastmsexam/2017/Spring2017/problem2.sas", file.path(biostat_Spring_2017_dir, "problem2.sas"))

download.file("https://raw.githubusercontent.com/esuess/msexam/master/pastmsexam/2017/Spring2017/heart.csv", file.path(biostat_Spring_2017_dir, "heart.csv"))

download.file("https://raw.githubusercontent.com/esuess/msexam/master/pastmsexam/2017/Spring2017/sales.txt", file.path(biostat_Spring_2017_dir, "sales.txt"))

download.file("https://raw.githubusercontent.com/esuess/msexam/master/pastmsexam/2017/Spring2017/breast.csv", file.path(biostat_Spring_2017_dir, "breast.csv"))
```


