---
title: "File Download for past MS exams"
output: html_notebook
---

# Past Statistics and Biostatistics MS exam data files

You can run this R notebook to download all of the past Statistics and Biostatistics MS exam data files.

The data files are downloaded from the MS Exam github repository.  [msexam](https://github.com/esuess/msexam/tree/master/pastmsexam)

```{r}
files <- list(
  
    d2018 = list( 
      df = list(url = "https://github.com/esuess/msexam/blob/master/pastmsexam/2018/Spring2018/",
        fs = list("ob_prob1.xlsx","sat_data.txt","lemon.csv","prob4.dat","BigMac.csv"),
        fb = list("ob_prob1.xlsx","sat_data.txt","lemon.csv","prob4.dat","uis.txt") ),
      ds = list(url = "https://github.com/esuess/msexam/blob/master/pastmsexam/2018/Spring2018/",
        ss = list("ob_prob1.csv","sat_data.txt","lemon.csv","prob4.dat","BigMac.csv"),
        sb = list("ob_prob1.csv","sat_data.txt","lemon.csv","prob4.dat","uis.txt") ) ),
  
    d2017 = list( 
      df = list(url = "https://github.com/esuess/msexam/blob/master/pastmsexam/2017/Fall2017/",
        fs = list("INJURY9.csv","river.csv","prostate.csv","prob4.txt","Jets.csv"),
        fb = list("INJURY9.csv","river.csv","prostate.csv","prob4.txt","valung.csv") ),
      ds = list(url = "https://github.com/esuess/msexam/blob/master/pastmsexam/2017/Spring2017/",
        ss = list("ob_prob1.xlsx","problem2.sas","heart.csv","sales.txt","Barley.csv"),
        sb = list("ob_prob1.xlsx","problem2.sas","heart.csv","sales.txt","breast.csv") ) ),
    
    d2016 = list(
      df = list(url = "https://github.com/esuess/msexam/blob/master/pastmsexam/2016/Fall2016/",
        fs = list("hypnotic_induction.csv","problem2.sas","mammography.csv","cars.txt","forest.csv"),
        fb = list("hypnotic_induction.csv","problem2.sas","mammography.csv","cars.txt","kidrecurr.txt") ),
      ds = list(url = "https://github.com/esuess/msexam/blob/master/pastmsexam/2016/Spring2016/",
      ss = list("cakemix.txt","problem2.csv","health.txt","DES_all.txt"),
      sb = list("cakemix.txt","problem2.csv","health.txt","selenium.csv") ) ),
    
    d2015 = list(
      df = list(url = "https://github.com/esuess/msexam/blob/master/pastmsexam/2015/Fall2015/",
        fs = list("problem1.sas","Expenditure.csv","reading.txt","prob4.dat","iris.xlsx","iris.jpg"),
        fb = list("problem1.sas","Expenditure.csv","reading.txt","prob4.dat","tongue_cancer.csv") ),
      ds = list(url = "https://github.com/esuess/msexam/blob/master/pastmsexam/2015/Spring2015/",
      ss = list("problem1.txt","problem1.MTW","salary.txt","ob_prob3.txt","prob4.dat","Survey_nonames_nocountry.xlsx","Survey_nonames_nocountry_corrected.xlsx"),
      sb = list("problem1.txt","problem1.MTW","salary.txt","ob_prob3.txt","prob4.dat","valung_small.csv") ) ),  
    
    d2014 = list(
      df = list(url = "https://github.com/esuess/msexam/blob/master/pastmsexam/2014/Fall2014/",
        fs = list("music.txt","sales.txt","Scout.txt","problem5.txt"),
        fb = list("music.txt","sales.txt","Scout.txt","SevAn.txt") ),
      ds = list(url = "https://github.com/esuess/msexam/blob/master/pastmsexam/2014/Spring2014/",
      ss = list("foodeffect.txt","reaction_time.txt","eld.txt","gamma.txt","mle2dgamma.R","problem5.txt"),
      sb = list("foodeffect.txt","reaction_time.txt","eld.txt","gamma.txt","mle2dgamma.R","phd.txt") ) ),
    
    d2013 = list(
      df = list(url = "https://github.com/esuess/msexam/blob/master/pastmsexam/2013/Fall2013/",
        fs = list("counts.txt","Concrete.xls","CHD.txt","logodds.R","problem5.txt"),
        fb = list("counts.txt","Concrete.xls","CHD.txt","logodds.R","valung.csv") ),
      ds = list(url = "https://github.com/esuess/msexam/blob/master/pastmsexam/2013/Spring2013/",
      ss = list("ob_prob1_bulbs.txt","ob_prob1_bulbs.xls","wealthy.csv","problem3.MTW","Weibull.R","ob_prob5_solid%20tumor.txt"),
      sb = list("ob_prob1_bulbs.txt","ob_prob1_bulbs.xls","wealthy.csv","Weibull.R","ob_prob5_solid%20tumor.txt") ) )
    
    
    
    
    
    
    
)



```





Specify the years of exams data file you wish to download.




First set the directory where you would like to download all of the files.

```{r}
download_dir <- "C:/Past_MS_Exams-CSUEB_Statistics_and_Biostatistics"

print(download_dir)
ifelse(!dir.exists(file.path(download_dir)), dir.create(file.path(download_dir)), 
       paste0("Directory already exists"))

#setwd(file.path(download_dir))

stat_dir <- file.path(download_dir, "Past_MS_Exams-Statistics")
stat_dir
biostat_dir <- file.path(download_dir, "Past_MS_Exams-Biostatistics")
biostat_dir

print(stat_dir)
ifelse(!dir.exists(file.path(stat_dir)), dir.create(file.path(stat_dir)), 
       paste0("Directory already exists"))

print(biostat_dir)
ifelse(!dir.exists(file.path(biostat_dir)), dir.create(file.path(biostat_dir)), 
       paste0("Directory already exists"))
```

Second create the subdirectories to download the files to.

```{r}
start_year <- 2013  #1998

end_year <- 2018


years <- (end_year-start_year+1)

test <- list("Fall", "Spring")

for (i in 1: length(test)){        # spring or fall
  for (j in end_year: start_year){ # year
    DIR <- paste0(j,"_",test[[i]])
    print(DIR)
    
    # Make Statistics subdirectories
    stat_dir_new <- file.path(stat_dir, DIR)
    print(stat_dir_new)
    ifelse(!dir.exists(file.path(stat_dir, DIR)), dir.create(file.path(stat_dir, DIR)), 
           print(paste0("Directory already exists")))
    
    for (k in 1: length(files[[(end_year-j+1)]][[i]][[(2)]])) {
        download.file( paste0(   files[[(end_year-j+1)]][[i]][[1]], paste0( files[[(end_year-j+1)]][[i]][[2]][[k]] )  ),
                          paste0(file.path(stat_dir, DIR ),"/",paste0(files[[(end_year-j+1)]][[i]][[2]][[k]]))   )
    }
  
    # Make Biostat subdirectories
    biostat_dir_new <- file.path(biostat_dir, DIR)
    print(biostat_dir_new)
    ifelse(!dir.exists(file.path(biostat_dir, DIR)), dir.create(file.path(biostat_dir, DIR)), 
           print(paste0("Directory already exists")))
    
    for (k in 1: length(files[[(end_year-j+1)]][[i]][[3]])) {
        download.file( paste0(   files[[(end_year-j+1)]][[i]][[1]], paste0( files[[(end_year-j+1)]][[i]][[3]][[k]] )  ),
                          paste0(file.path(biostat_dir, DIR ),"/",paste0(files[[(end_year-j+1)]][[i]][[3]][[k]]))   )
    }
}
}

```
```






