---
title: "File Download for past MS exams"
output: html_notebook
---

# Past Statistics and Biostatistics MS exam data files

You can run this R notebook to download all of the past Statistics and Biostatistics MS exam data files.

The data files are downloaded from the MS Exam github repository.  [msexam](https://github.com/esuess/msexam/tree/master/pastmsexam)

```{r}
files <- list(
    d2018 = list( 
      ss = list("ob_prob1.csv","sat_data.txt","lemon.csv","prob4.dat","BigMac.csv"),
      sb = list("ob_prob1.csv","sat_data.txt","lemon.csv","prob4.dat","uis.txt") ),
  
    d2017 = list( 
      fs = list("INJURY9.csv","river.csv","prostate.csv","prob4.txt","Jets.csv"),
      fb = list("INJURY9.csv","river.csv","prostate.csv","prob4.txt","valung.csv"),
      ss = list("ob_prob1.xlsx","problem2.sas","heart.csv","sales.txt","Barley.csv"),
      sb = list("ob_prob1.xlsx","problem2.sas","heart.csv","sales.txt","breast.csv") ),
    
    d2016 = list(
      fs = list("hypnotic_induction.csv","problem2.sas","mammo.csv","cars.txt","forest.csv"),
      fb = list("hypnotic_induction.csv","problem2.sas","mammo.csv","cars.txt","kidrecurr.txt"),
      ss = list("cakemix.txt","problem2.csv","health.txt","DES_all.txt"),
      sb = list("cakemix.txt","problem2.csv","health.txt","selenium.csv")
    )
)

```





Specify the years of exams data file you wish to download.

```{r}
start_year <- 2017  #1998

end_year <- 2018

```

First set the directory where you would like to download all of the files.

```{r}
download_dir <- "C:/Past_MS_Exams-CSUEB_Statistics_and_Biostatistics"

print(download_dir)
ifelse(!dir.exists(file.path(download_dir)), dir.create(file.path(download_dir)), 
       paste0("Directory already exists"))

#setwd(file.path(download_dir))

stat_dir <- file.path(download_dir, "Past_MS_Exams-Statistics")
biostat_dir <- file.path(download_dir, "Past_MS_Exams-Biostatistics")


print(stat_dir)
ifelse(!dir.exists(file.path(stat_dir)), dir.create(file.path(stat_dir)), 
       paste0("Directory already exists"))

print(biostat_dir)
ifelse(!dir.exists(file.path(biostat_dir)), dir.create(file.path(biostat_dir)), 
       paste0("Directory already exists"))
```

Second create the subdirectories to download the files to.

```{r}
#stat_dir
#biostat_dir

test <- list("_Spring", "_Fall")

for (i in 1: length(test)){
  for (j in start_year: end_year){
    DIR <- paste0(j,test[[i]])
    print(DIR)
    
    # Make Statistics subdirectories
    stat_dir_new <- file.path(stat_dir, DIR)
    print(stat_dir_new)
    ifelse(!dir.exists(file.path(stat_dir, DIR)), dir.create(file.path(stat_dir, DIR)), 
           print(paste0("Directory already exists")))
    
    
    
    
    
    
    # Make Biostat subdirectories
    biostat_dir_new <- file.path(biostat_dir, DIR)
    print(biostat_dir_new)
    ifelse(!dir.exists(file.path(biostat_dir, DIR)), dir.create(file.path(biostat_dir, DIR)), 
           print(paste0("Directory already exists")))
  }
}
```




```{r}

```






### MS Exam, Biostatistics, Spring 2018

```{r}

files <- list(
    d2018 = list( 
      ss = list("ob_prob1.csv", "sat_data.txt", "lemon.csv", "prob4.dat", "BigMac.csv"),
      sb = list("ob_prob1.csv", "sat_data.txt", "lemon.csv", "prob4.dat") ),
  
    d2017 = list( 
      fs = list("INJURY9.csv", "river.csv", "prostate.csv", "prob4.txt", "Jets.csv"),
      fb = list("INJURY9.csv", "river.csv", "prostate.csv", "prob4.txt", "valung.csv"),
      ss = list("ob_prob1.xlsx", "problem2.sas", "heart.csv", "sales.txt", "Barley.csv"),
      sb = list("ob_prob1.xlsx", "problem2.sas", "heart.csv", "sales.txt", "breast.csv") )
)
  
files
files$d2018$ss[[1]]

stat_Spring_2018_dir <-"C:\\Past_MS_Exams-CSUEB_Statistics_and_Biostatistics\\Past_MS_Exams-Statistics\\2018_Spring"


for ( i in 1: length(files)){ 
  download.file(paste0("https://raw.githubusercontent.com/esuess/msexam/master/pastmsexam/2018/Spring2018/", paste0(files[[i]]) ),
                file.path(stat_Spring_2018_dir, paste0(files[[i]]) ) )
}

download.file("https://raw.githubusercontent.com/esuess/msexam/master/pastmsexam/2018/Spring2018/ob_prob1.csv", file.path(stat_Spring_2018_dir, "ob_prob1.csv"))

download.file("https://raw.githubusercontent.com/esuess/msexam/master/pastmsexam/2018/Spring2018/sat_data.txt", file.path(stat_Spring_2018_dir, "sat_data.txt"))

download.file("https://raw.githubusercontent.com/esuess/msexam/master/pastmsexam/2018/Spring2018/lemon.csv", file.path(stat_Spring_2018_dir, "lemon.csv"))

download.file("https://raw.githubusercontent.com/esuess/msexam/master/pastmsexam/2018/Spring2018/prob4.dat", file.path(stat_Spring_2018_dir, "prob4.dat"))

download.file("https://raw.githubusercontent.com/esuess/msexam/master/pastmsexam/2018/Spring2018/BigMac.csv", file.path(stat_Spring_2018_dir, "BigMac.csv"))


download.file("https://raw.githubusercontent.com/esuess/msexam/master/pastmsexam/2018/Spring2018/ob_prob1.csv", file.path(biostat_Spring_2018_dir, "ob_prob1.csv"))

download.file("https://raw.githubusercontent.com/esuess/msexam/master/pastmsexam/2018/Spring2018/sat_data.txt", file.path(biostat_Spring_2018_dir, "sat_data.txt"))

download.file("https://raw.githubusercontent.com/esuess/msexam/master/pastmsexam/2018/Spring2018/lemon.csv", file.path(biostat_Spring_2018_dir, "lemon.csv"))

download.file("https://raw.githubusercontent.com/esuess/msexam/master/pastmsexam/2018/Spring2018/prob4.dat", file.path(biostat_Spring_2018_dir, "prob4.dat"))

download.file("https://raw.githubusercontent.com/esuess/msexam/master/pastmsexam/2018/Spring2018/uis.txt", file.path(biostat_Spring_2018_dir, "uis.txt"))
```



### MS Exam, Statistics, Fall 2017

```{r}
download.file("https://raw.githubusercontent.com/esuess/msexam/master/pastmsexam/2017/Fall2017/INJURY9.csv", file.path(stat_Fall_2017_dir, "INJURY9.csv"))

download.file("https://raw.githubusercontent.com/esuess/msexam/master/pastmsexam/2017/Fall2017/river.csv", file.path(stat_Fall_2017_dir, "river.csv"))

download.file("https://raw.githubusercontent.com/esuess/msexam/master/pastmsexam/2017/Fall2017/prostate.csv", file.path(stat_Fall_2017_dir, "prostate.csv"))

download.file("https://raw.githubusercontent.com/esuess/msexam/master/pastmsexam/2017/Fall2017/prob4.txt", file.path(stat_Fall_2017_dir, "prob4.txt"))

download.file("https://raw.githubusercontent.com/esuess/msexam/master/pastmsexam/2017/Fall2017/Jets.csv", file.path(stat_Fall_2017_dir, "Jets.csv"))


download.file("https://raw.githubusercontent.com/esuess/msexam/master/pastmsexam/2017/Fall2017/INJURY9.csv", file.path(biostat_Fall_2017_dir, "INJURY9.csv"))

download.file("https://raw.githubusercontent.com/esuess/msexam/master/pastmsexam/2017/Fall2017/river.csv", file.path(biostat_Fall_2017_dir, "river.csv"))

download.file("https://raw.githubusercontent.com/esuess/msexam/master/pastmsexam/2017/Fall2017/prostate.csv", file.path(biostat_Fall_2017_dir, "prostate.csv"))

download.file("https://raw.githubusercontent.com/esuess/msexam/master/pastmsexam/2017/Fall2017/prob4.txt", file.path(biostat_Fall_2017_dir, "prob4.txt"))

download.file("https://raw.githubusercontent.com/esuess/msexam/master/pastmsexam/2017/Fall2017/valung.csv", file.path(biostat_Fall_2017_dir, "valung.csv"))

```

### MS Exam, Biostatistics, Spring 2017

```{r}
download.file("https://raw.githubusercontent.com/esuess/msexam/master/pastmsexam/2017/Spring2017/ob_prob1.csv", file.path(stat_Spring_2017_dir, "ob_prob1.csv"))

download.file("https://raw.githubusercontent.com/esuess/msexam/master/pastmsexam/2017/Spring2017/problem2.sas", file.path(stat_Spring_2017_dir, "problem2.sas"))

download.file("https://raw.githubusercontent.com/esuess/msexam/master/pastmsexam/2017/Spring2017/heart.csv", file.path(stat_Spring_2017_dir, "heart.csv"))

download.file("https://raw.githubusercontent.com/esuess/msexam/master/pastmsexam/2017/Spring2017/sales.txt", file.path(stat_Spring_2017_dir, "sales.txt"))

download.file("https://raw.githubusercontent.com/esuess/msexam/master/pastmsexam/2017/Spring2017/Barley.csv", file.path(stat_Spring_2017_dir, "Barley.csv"))


download.file("https://raw.githubusercontent.com/esuess/msexam/master/pastmsexam/2017/Spring2017/ob_prob1.csv", file.path(biostat_Spring_2017_dir, "ob_prob1.csv"))

download.file("https://raw.githubusercontent.com/esuess/msexam/master/pastmsexam/2017/Spring2017/problem2.sas", file.path(biostat_Spring_2017_dir, "problem2.sas"))

download.file("https://raw.githubusercontent.com/esuess/msexam/master/pastmsexam/2017/Spring2017/heart.csv", file.path(biostat_Spring_2017_dir, "heart.csv"))

download.file("https://raw.githubusercontent.com/esuess/msexam/master/pastmsexam/2017/Spring2017/sales.txt", file.path(biostat_Spring_2017_dir, "sales.txt"))

download.file("https://raw.githubusercontent.com/esuess/msexam/master/pastmsexam/2017/Spring2017/breast.csv", file.path(biostat_Spring_2017_dir, "breast.csv"))
```


